\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
caption corrected
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64963 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{minipage}{0.5\linewidth}
%\includegraphics[width=\textwidth]{fire}
% TODO: Something from Europe
\end{minipage}
}

>>>>

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{fire_valencia_040914}
The event in the figure refers to a major wildfire occurred near Valencia on June 28th 2012 and 
under control on July 4th. The actual perimeters recorded by the JRC-EFFIS team are shown, in 
comparison with the simulated burnt area obtained in GRASS.
\end{minipage}
}
